Where Do Population III Stars Form?

### 2019-04-11 paper.tex
Revising halo variation discussion

%====================================================================
\subsection{Variations in the halo masses at collapse}
%====================================================================
The collapse of gas that goes on to form Pop III stars occurs in a wide range of host halo masses across time. There are three main reasons why the host halo masses may vary significantly. First, a generation of metal-free stars can form if their progenitors had only formed stars that did not go supernova. This prevents metals from enriching the environment which would stop metal-free star formation and begin metal-enriched star formation. Second, dynamical heating from mergers and accretion can heat the gas within halos and prevent \hh{} regions from cooling. This would delay star formation in halos at early times \citep{Yoshida03}. Finally, temporal fluctuations in the local Lyman-Werner radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool. While this may only be a small affect in some halos where the local Lyman-Werner radiation is relatively low, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active Pop III star formation sites. The combination of these three processes will determine which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.

>>>>

%====================================================================
\subsection{Variations in the halo masses at collapse}
%====================================================================
Previous studies have focused on the minimum halo mass of Pop III hosts as a function of Lymer-Werner intensity and often in halos up to an order of magnitude greater than the mininum.  We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation. There are three main causes of this significant variation in mass. First, a fraction of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.  Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs. Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.  Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently \hh{} cooling. This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situtation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}. Finally, temporal fluctuations in the local Lyman-Werner radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool. While this may only be a small effect in some halos where the local Lyman-Werner radiation flucutations is relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.  In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.  The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.
